Universal and varying leadership dimensions across human societies

### 2020-06-24 leadership_across_cultures_contexts.Rmd
RE-RE Submisson version

---
title: "Leadership across cultures and contexts: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

@@

<!-- * Leadership across human societies -->
<!-- * Human leadership: the determinants of leaders across cultures -->
<!-- * Leaders and followers across human societies -->
<!-- * Leadership across cultures and contexts -->
<!-- * The determinants of leadership across cultures and contexts -->
<!-- * The determinants of human leadership across societies -->

@@

Our candidate universal dimensions appear in the computational services model [@hagen_leadership_2019], in which knowledgeable and intelligent individuals provide computational (cognitive) services (e.g., conflict resolution, strategizing) to group members in exchange for a variety of fitness benefits [see also @garfield_evolutionary_2019]. This model emphasizes mating benefits, however, which appear in `r matingbenefit`% of cultures, below our arbitrary 60% threshold for "universality" (Figure \@ref(fig:varsupportcb)). But there was evidence for the *Social, reproductive, and materials success* feature, which included polygynous leaders, having a high-quality spouse, and having many children, in more cultures (`r reprosuccess`%) than other features (Figure \@ref(fig:featuressupportplot)). Interestingly, the computational services model highlights women's family leadership role, and there was more evidence for the *Social, reproductive, and materials success* feature for females leaders than male leaders (Figure S\@ref(fig:heatmapfeaturesex)), with the caveat that there were few text records on female leaders in our sample.

>>>>

---
title: "Universal and varying leadership dimensions across human societies"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2:
    number_sections: true
bibliography: Leader2.bib
csl: apa-6th-edition.csl
---

@@

<!-- * Leadership across human societies -->
<!-- * Human leadership: the determinants of leaders across cultures -->
<!-- * Leaders and followers across human societies -->
<!-- * Leadership across cultures and contexts -->
<!-- * The determinants of leadership across cultures and contexts -->
<!-- * The determinants of human leadership across societies -->
<!-- * Universal and varying leadership traits across 59 traditional cultures -->
<!-- * Analysis of 109 leadership traits across 59 traditional cultures -->

@@

Our candidate universal dimensions appear in the computational services model [@hagen_leadership_2019], in which knowledgeable and intelligent individuals provide computational (cognitive) services (e.g., conflict resolution, strategizing) to group members in exchange for a variety of fitness benefits [see also @garfield_evolutionary_2019]. This model emphasizes mating benefits, however, which appear in `r matingbenefit`% of cultures, below our arbitrary 60% threshold for "universality" (Figure \@ref(fig:varsupportcb)). But there was evidence for the *Social, reproductive, and materials success* feature, which included polygynous leaders, having a high-quality spouse, and having many children, in more cultures (`r reprosuccess`%) than other features (Figure \@ref(fig:featuressupportplot)). Interestingly, the computational services model highlights women's family leadership role, and there was proportionally more evidence for the *Social, reproductive, and materials success* feature among females leaders than male leaders (Figure S\@ref(fig:heatmapfeaturesex)), with the caveat that there were few text records on female leaders in our sample.
